Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s}$ =13 TeV

### 2020-05-06 sec_ana.tex

Delivery of protons with world-highest energy by LHC at CERN makes it possible to generate various phenomena from their collisions. Recent center-of-mass energy of colliding two protons is increased up to $\sqrt{\it{s}} =$ \unit[13]{TeV} during LHC Run2 period. Among data from proton-proton collisions at \unit[13]{TeV}, This paper describes analysis results obtained by using 2016 to 2018 data sets. The full description of ALICE detector in the LHC Run 2 can be found in Ref. \cite{ALICEdet}. The present analysis mainly uses V0(\cite{VZEROpaper}), ITS (Inner Tracking System, \cite{ITSpaper}) and TPC (Time Projection Chamber, \cite{TPCpaper}) detectors.

>>>>

Delivery of protons with world-highest energy by LHC at CERN makes it possible to generate various phenomena from their collisions. Recent center-of-mass energy of colliding two protons is increased up to $\sqrt{\it{s}}$~=~\unit[13]{TeV} during LHC Run2 period. Among data from proton-proton collisions at \unit[13]{TeV}, This paper describes analysis results obtained by using 2016 to 2018 data sets. The full description of ALICE detector in the LHC Run 2 can be found in Refs. \cite{Aamodt:2008zz,Abelev:2014ffa}. The present analysis mainly uses V0~\cite{Abbas:2013taa}, ITS (Inner Tracking System)~\cite{aliceITS} and TPC (Time Projection Chamber)~\cite{aliceTPC} detectors.
